State of the Practice for Lattice Boltzmann Method Software

### 2022-04-25 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
Revisions to Section 2.1, fixed verb tense

We developed a methodology for evaluating the state of the practice of research
software \citep{SmithEtAl2021, SmithAndMichalski2022} and applied it to the
specific domain of LBM software.  Since we group best practices around
conventional software qualities, the first section below provides definitions
for the qualities of interest (Section~\ref{softwarequalities}), along with
information on how to measure these qualities. The following section
(Section~\ref{Sec_OverallProcess}) provides an overview of the steps we used to
select, measure and compare LBM software.  The remaining sections provide
details on each step in the methodology.

@@

	\item[Usability] Usability is measured by the extent to which a software
	product can be used by specified users to achieve specified goals with
	effectiveness, efficiency, and satisfaction in a specified context of use
	\citep{nielsonusability}. We assumed that high usability correlates with
	the presence of documentation, including tutorials, manuals, defined
	user characteristics, and user support. Preferably the user support model
	will have avenues to contact developers and report issues.

	\item[Maintainability] A measure of maintainability is the effort with which
	a software system or component can be modified to correct faults, improve
	performance or other attributes, and satisfy new requirements
	\citep{IEEEStdGlossarySET1990, boehm2007software}. In the current work, we
	measure maintainability by the quality of the documentation and the presence
	of version control and issue tracking. There are many documentation
	artifacts that can improve maintainability, including user and developer
	manuals, specifications, README files, change logs, release notes,
	publications, forums, and instructional websites. We also asked developers
	if they considered the ease of future changes when developing the software
	packages.

@@

	\item[Reproducibility] Software achieves reproducibility if another
	developer can take the original code and input data, run it, and obtain the
	original output \citep{BenureauAndRougier2017}. We measured reproducibility
	qualitatively by asking developers if they have any concerns that their
	computational results won't be reproducible and if they have taken any
	steps to ensure reproducibility.

>>>>

We apply our methodology for evaluating the state of the practice of research
software \citep{SmithEtAl2021, SmithAndMichalski2022} to the specific domain of
LBM software.  Since we group best practices around conventional software
qualities, the first section below provides definitions for the qualities of
interest (Section~\ref{softwarequalities}), along with information on how to
measure these qualities. The following section
(Section~\ref{Sec_OverallProcess}) provides an overview of the steps we used to
select, measure and compare LBM software.  The remaining sections
(Sections~\ref{identifysoftware} to~\ref{SecDomainAnalysis}) provide details on
each step in the methodology.

@@

	\item[Usability] Usability is measured by the extent to which a software
	product can be used by specified users to achieve specified goals with
	effectiveness, efficiency, and satisfaction in a specified context of use
	\citep{nielsonusability}. We assume that high usability correlates with
	the presence of documentation, including tutorials, manuals, defined
	user characteristics, and user support. Preferably the user support model
	will have avenues to contact developers and report issues.

	\item[Maintainability] A measure of maintainability is the effort with which
	a software system or component can be modified to correct faults, improve
	performance or other attributes, and satisfy new requirements
	\citep{IEEEStdGlossarySET1990, boehm2007software}. In the current work, we
	measure maintainability by the quality of the documentation and the presence
	of version control and issue tracking. There are many documentation
	artifacts that can improve maintainability, including user and developer
	manuals, specifications, README files, change logs, release notes,
	publications, forums, and instructional websites. We also ask developers
	if they considered the ease of future changes when developing their
	software.

@@

	\item[Reproducibility] Software achieves reproducibility if another
	developer can take the original code and input data, run it, and obtain the
	original output \citep{BenureauAndRougier2017}. We measure reproducibility
	qualitatively by asking developers if they have any concerns that their
	computational results are not reproducible, and if they have taken any
	steps to ensure reproducibility.
